Comparison of FDR methods on 16S microbiome data with SummarizedBenchmark

### 2018-01-19 datasets/microbiome/microbiome-SummarizedBenchmark.Rmd
Add covariate boxplot

@@

```{r, goodrich-genus-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```

@@

```{r, baxter-genus-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```

>>>>

```{r, schubert-genus-covariates}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots( sb, alpha=0.1, nsets=6, methods=methods)
```

@@

```{r, goodrich-genus-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r, goodrich-genus-covariates}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots( sb, alpha=0.1, nsets=6, methods=methods)
```

@@

```{r, baxter-genus-overlap}
plotFDRMethodsOverlap(sb, alpha=0.1, supplementary=FALSE, order.by="freq", nsets=100 )
```
```{r}
methods <- c( "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf" )
plotCovariateBoxplots( sb, alpha=0.1, nsets=6, methods=methods)
```
